An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-23 Revision/response.tex

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
	\caption{}
	\label{fig:attribute_selectivity}
\end{figure}

\textcolor{blue}{"The proximity of the four curves (representing different attribute distributions) in the figure reflects algorithm sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts. Conversely, greater divergence among the curves indicates higher distributional dependence. Accordingly, the "Strong" label signifies robust performance consistency across varying distributions, while "Weak" denotes pronounced performance fluctuations under distributional changes."}

%%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run experiments with multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{metarevision}
}

\noindent
\textbf{Response:} We believe this is an excellent suggestion. In fact, in the initial version of our paper, we use the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms. In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two. Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness. \textbf{(Please refer to the last paragraph of Section 4.2.3 and the green highlighted part in Section 4.3.3.)}

To further enrich the evaluation of complex multimodal queries, we add new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4. Specifically, we construct a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set. We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms. The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

### 2025-07-23 VLDB2026/main.tex
Update main.tex

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB). At the same time, we can see that some algorithms (e.g., SeRF, ACORN-1) perform even worse than the VBASE database, which indicates that they do not adapt well to large-scale dataset scenarios. Although Milvus has a low QPS, it can achieve a recall of 1 with an excellent memory footprint of around 80GB}.

>>>>

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, in the 100-million-scale dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption (300-400GB).  Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms.}.
